Moral Foundations of U.S. Political News Organizations

### 2019-03-25 pilot_manuscript.Rmd
updated the graph and saved you a picture

```{r exp1 source descriptives, results = 'asis', echo = FALSE}

@@

@@

#Get the final dataset split into the 4 sources
final$Source = as.factor(final$Source)
NYtimesDesc1 = subset(final, Source == "NY Times") #number of obs. = number of articles for that source; NYT = 406
NPRDesc1 = subset(final, Source == "NPR") #NPR = 695 articles
FoxDesc1 = subset(final, Source == "Fox News") #Fox = 503 articles
BreitbartDesc1 = subset(final, Source == "Breitbart") #Breitbart = 1,437 articles

##Add valence
#NY Times
NYTimes_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)

for (i in 1:nrow(NYtimesDesc1)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(NYtimesDesc1$stemmed[i], " "))))

#only pull the words in the dataset for each foundation
#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]

#add to the dataset
temp2$URL = NYtimesDesc1$Url[i]
temp2$Source = NYtimesDesc1$Source[i]
temp2$wordcount = NYtimesDesc1$wordcount[i]
temp2$Text = NYtimesDesc1$Text[i]

#bind with original
NYTimes_final_desc = rbind(NYTimes_final_desc, temp2)
}

NYTimes_final_desc$valence = vlookup(NYTimes_final_desc$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#NPR
NPR_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)

for (i in 1:nrow(NPRDesc1)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(NPRDesc1$stemmed[i], " "))))

#only pull the words in the dataset for each foundation
#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]

#add to the dataset
temp2$URL = NPRDesc1$Url[i]
temp2$Source = NPRDesc1$Source[i]
temp2$wordcount = NPRDesc1$wordcount[i]
temp2$Text = NPRDesc1$Text[i]

#bind with original
NPR_final_desc = rbind(NPR_final_desc, temp2)
}

NPR_final_desc$valence = vlookup(NPR_final_desc$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#Fox News
Fox_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)

for (i in 1:nrow(FoxDesc1)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(FoxDesc1$stemmed[i], " "))))

#only pull the words in the dataset for each foundation
#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]

#add to the dataset
temp2$URL = FoxDesc1$Url[i]
temp2$Source = FoxDesc1$Source[i]
temp2$wordcount = FoxDesc1$wordcount[i]
temp2$Text = FoxDesc1$Text[i]

#bind with original
Fox_final_desc = rbind(Fox_final_desc, temp2)
}

Fox_final_desc$valence = vlookup(Fox_final_desc$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#Breitbart
Breitbart_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)

for (i in 1:nrow(BreitbartDesc1)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(BreitbartDesc1$stemmed[i], " "))))

#only pull the words in the dataset for each foundation
#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]

#add to the dataset
temp2$URL = BreitbartDesc1$Url[i]
temp2$Source = BreitbartDesc1$Source[i]
temp2$wordcount = BreitbartDesc1$wordcount[i]
temp2$Text = BreitbartDesc1$Text[i]

#bind with original
Breitbart_final_desc = rbind(Breitbart_final_desc, temp2)
}

Breitbart_final_desc$valence = vlookup(Breitbart_final_desc$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

##Eliminate NAs
NYTimes_final_desc = na.omit(NYTimes_final_desc)
NPR_final_desc = na.omit(NPR_final_desc)
Fox_final_desc = na.omit(Fox_final_desc)
Breitbart_final_desc = na.omit(Breitbart_final_desc)

#Calculate mean valence by source
NYTimes_valence_mean = mean(NYTimes_final_desc$valence)
NPR_valence_mean = mean(NPR_final_desc$valence)
Fox_valence_mean = mean(Fox_final_desc$valence)
Breitbart_valence_mean = mean(Breitbart_final_desc$valence)

```
overall valence for each source

@@

>>>>

```{r exp1 source descriptives, results = 'asis', echo = FALSE, message = F}

@@

  final$valenceavg[i] = mean(tempwords$tempval, na.rm = T)

@@

tapply(final$valenceavg, final$Source, mean)
tapply(final$valenceavg, final$Source, sd)
tapply(final$wordcount, final$Source, mean)
tapply(final$wordcount, final$Source, sd)
tapply(final$uniquewords, final$Source, mean)
tapply(final$uniquewords, final$Source, sd)
tapply(final$Source, final$Source, length)
tapply(final$wordcount, final$Source, sum)

library(quanteda)

final$FK = NA

for (i in 1:nrow(final)){
  final$FK[i] = unlist(textstat_readability(final$Text[i], 
                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
}

tapply(final$FK, final$Source, mean)
tapply(final$FK, final$Source, sd)

overall valence for each source

@@

```{r conference-pic, eval = F, include = F}
library(ggplot2)
library(reshape)

cleanup = theme(panel.grid.major = element_blank(), 
                panel.grid.minor = element_blank(), 
                panel.background = element_blank(), 
                axis.line.x = element_line(color = "black"),
                axis.line.y = element_line(color = "black"),
                legend.key = element_rect(fill = "white"),
                text = element_text(size = 10))

graphdata = as.data.frame(tableprint)
graphlong = melt(graphdata[ , c(1,2,4)], 
                 id = "Foundation")
graphlong2 = melt(graphdata[ , c(1, 3,5)],
                  id = "Foundation",
                  measured = c("SD_C", "SD_L"))
graphlong$sd = graphlong2$value
graphlong$lower = as.numeric(as.character(graphlong$value)) - 2*as.numeric(as.character(graphlong$sd))
graphlong$upper = as.numeric(as.character(graphlong$value)) + 2*as.numeric(as.character(graphlong$sd))

graphlong$value = as.numeric(as.character(graphlong$value))

graph_data = ggplot(graphlong, aes(Foundation, value, color = variable)) + 
  geom_point(position = position_dodge(width = 0.90)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                position = position_dodge(width = 0.90),
                width = .2) + 
  cleanup +
  ylab("Mean Weighted Valence") + 
  scale_color_manual(values = c("red", "blue"),
                       labels = c("Conservative", "Liberal"),
                       name = "Party") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + 
  geom_hline(yintercept = 0, linetype = 1, color = "black")

tiff(filename = "exp1_graph.tiff", res = 300, width = 4, 
     height = 3, units = 'in', compression = "lzw")
plot(graph_data)
dev.off()
